Jaigo Technical Report

### 2007-12-19 paper/paper.tex
label units

\begin{table}
  \rotatebox{90}{
    \begin{tabular}{ccccccccc} \toprule
      Function & Calls & Percent & Own Time & Time & Avg & Min & Max & File\\	\midrule
      (no name) &	404494 &	32.8 &	71255.203 &	147518.241 &	0.365 &	0.059 &	1650.149 &	simple\_go.js (line 407)\\
      flood\_mark &	3838 &	15.94 &	34634.022 &	96713.52 &	25.199 &	0.206 &	1736.537 &	simple\_go.js (line 807)\\
      iterate &	404495 &	8.75 &	19004.696 &	76254.33 &	0.189 &	0.011 &	1650.101 &	simple\_go.js (line 391)\\
      (no name) &	735190 &	8.72 &	18941.197 &	18941.987 &	0.026 &	0.008 &	1572.648 &	simple\_go.js (line 819)\\
      string\_as\_move &	242765 &	5.86 &	12724.373	& 12725.279 &	0.052 &	0.011 &	1629.186 &	simple\_go.js (line 192)\\
      (no name) &	1041519 &	4.7 &	10209.513 &	57248.372 &	0.055 &	0.015 &	1649.869 &	simple\_go.js (line 416)\\
      List\_Block\_Liberties &	7706 &	4.02 &	8727.331 &	21457.809 &	2.785 &	0.013 &	1630.607 &	simple\_go.js (line 863)\\
      iterateOwnProperties &	14752 &	3.68 &	7985.019 &	9340.503 &	0.633 &	0.004 &	2.419 &	simple\_go.js (line 132)\\
      update &	8742 &	3.18 &	6911.102 &	6911.93 &	0.791 &	0.004 &	1648.007 &	simple\_go.js (line 117)\\
      Calculate\_Neighbour &	661 &	3.03 &	6593.032 &	60385.478 &	91.355 &	0.115 &	1679.244 &	simple\_go.js (line 829)\\
      (no name) &	160414 &	2.51 &	5444.827 &	5445.809 &	0.034	& 0.008 &	944.464 &	simple\_go.js (line 835)\\
      Add\_Stone &	6010 &	1.1 &	2392.214	& 191461.602	& 31.857 &	1.524 &	1785.447 &	simple\_go.js (line 641)\\ \bottomrule
    \end{tabular}}
  \caption{First 100 moves on a 19x19 board}
  \label{table:first100}
\end{table}

>>>>

\begin{table}
  \rotatebox{90}{
    \begin{tabular}{ccccccccc} \toprule
      Function & Calls & Percent & Own Time (ms) & Time (ms) & Avg (ms) & Min (ms) & Max (ms) & File\\	\midrule
      (no name) &	404494 &	32.8 &	71255.203 &	147518.241 &	0.365 &	0.059 &	1650.149 &	simple\_go.js (line 407)\\
      flood\_mark &	3838 &	15.94 &	34634.022 &	96713.52 &	25.199 &	0.206 &	1736.537 &	simple\_go.js (line 807)\\
      iterate &	404495 &	8.75 &	19004.696 &	76254.33 &	0.189 &	0.011 &	1650.101 &	simple\_go.js (line 391)\\
      (no name) &	735190 &	8.72 &	18941.197 &	18941.987 &	0.026 &	0.008 &	1572.648 &	simple\_go.js (line 819)\\
      string\_as\_move &	242765 &	5.86 &	12724.373	& 12725.279 &	0.052 &	0.011 &	1629.186 &	simple\_go.js (line 192)\\
      (no name) &	1041519 &	4.7 &	10209.513 &	57248.372 &	0.055 &	0.015 &	1649.869 &	simple\_go.js (line 416)\\
      List\_Block\_Liberties &	7706 &	4.02 &	8727.331 &	21457.809 &	2.785 &	0.013 &	1630.607 &	simple\_go.js (line 863)\\
      iterateOwnProperties &	14752 &	3.68 &	7985.019 &	9340.503 &	0.633 &	0.004 &	2.419 &	simple\_go.js (line 132)\\
      update &	8742 &	3.18 &	6911.102 &	6911.93 &	0.791 &	0.004 &	1648.007 &	simple\_go.js (line 117)\\
      Calculate\_Neighbour &	661 &	3.03 &	6593.032 &	60385.478 &	91.355 &	0.115 &	1679.244 &	simple\_go.js (line 829)\\
      (no name) &	160414 &	2.51 &	5444.827 &	5445.809 &	0.034	& 0.008 &	944.464 &	simple\_go.js (line 835)\\
      Add\_Stone &	6010 &	1.1 &	2392.214	& 191461.602	& 31.857 &	1.524 &	1785.447 &	simple\_go.js (line 641)\\ \bottomrule
    \end{tabular}}
  \caption{First 100 moves on a 19x19 board}
  \label{table:first100}
\end{table}
